Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-30 dit-paper_ieee.tex
go go gadgeto commit

	\subsection{Simulation}

@@

	We observe that the more we are close to the implicit deadline case, the less systems have FPDIT. This is easily explained by the fact that a lower CDF means more idle instant for each task, and thus more opportunities for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to happen, a higher number of tasks results in a decrease in FPDIT density.

@@

	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
	three tasks without synchronous instants were generated. The size of their
	C-space (number of valid WCET vectors) was calculated and compared with that of the same
	task sets with all offsets set to zero. In other words, this figure
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.

>>>>

	\subsection{Simulation}
	\label{sct:noFPDITsimu}

@@

	We observe that the more we are close to the implicit deadline case ($CDF = 0$), the less systems have FPDIT. This is easily explained by the fact that a lower CDF means more idle instant for each task, and thus more opportunities for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to happen, a higher number of tasks results in a decrease in FPDIT density.

@@

	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
	three tasks without synchronous instants were generated. The size of their
	C-space (number of valid WCET vectors) was compared with that of the same
	task sets with all offsets set to zero. The systems were generated as in section~\ref{sct:noFPDITsimu}
	and the integer linear problems used to remove redundancies were solved via the GLPK tool\footnote{\url{http://www.gnu.org/software/glpk/}}.

	In other words, this figure
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.
